Evaluating Variable Importances

### 2019-04-08 Scripts/evaluating_variable_importances.Rmd
edits to results scripts
editting script for variable importances
editted results script

>>>>

## Variable Importance Heatmaps for models with distance type predictors (Ranks)

### SMOTE

```{r}
#GM12878

rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_10kb_SMOTE$Feature)
rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_25kb_SMOTE$Feature)
rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_50kb_SMOTE$Feature)
rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_100kb_SMOTE$Feature)

vim.gm12878.smote <- data.frame(Feature=unionannots)

vim.gm12878.smote <- left_join(left_join(left_join(left_join(vim.gm12878.smote,rfimpvars_gm12878_10kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_25kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_50kb_SMOTE, by="Feature"),
								rfimpvars_gm12878_100kb_SMOTE, by="Feature")
names(vim.gm12878.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")

vim.gm12878.smote.ranks <- data.frame(Feature=vim.gm12878.smote$Feature,
									  Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
									  Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
									  Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
									  Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))

rankdata <- cbind(vim.gm12878.smote.ranks$Rank.10kb,
                  vim.gm12878.smote.ranks$Rank.25kb,
				  vim.gm12878.smote.ranks$Rank.50kb,
				  vim.gm12878.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.gm12878.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")

#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
heatmap.2(t(rankdata),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          #margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 2,
          dendrogram="both",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = TRUE,
          cexRow=1.5,
          cexCol=0.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=1:4,
          colsep=0:nrow(rankdata))

#K562

rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

rfimpvars_K562_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_10kb_SMOTE$Feature)
rfimpvars_K562_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_25kb_SMOTE$Feature)
rfimpvars_K562_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_50kb_SMOTE$Feature)
rfimpvars_K562_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_100kb_SMOTE$Feature)

vim.K562.smote <- data.frame(Feature=unionannots)

vim.K562.smote <- left_join(left_join(left_join(left_join(vim.K562.smote,rfimpvars_K562_10kb_SMOTE, by="Feature"),
								rfimpvars_K562_25kb_SMOTE, by="Feature"),
								rfimpvars_K562_50kb_SMOTE, by="Feature"),
								rfimpvars_K562_100kb_SMOTE, by="Feature")
names(vim.K562.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")

vim.K562.smote.ranks <- data.frame(Feature=vim.K562.smote$Feature,
									  Rank.10kb=rank(-vim.K562.smote$Importance.10kb, na.last = TRUE),
									  Rank.25kb=rank(-vim.K562.smote$Importance.25kb, na.last = TRUE),
									  Rank.50kb=rank(-vim.K562.smote$Importance.50kb, na.last = TRUE),
									  Rank.100kb=rank(-vim.K562.smote$Importance.100kb, na.last = TRUE))

rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
                  vim.K562.smote.ranks$Rank.25kb,
				  vim.K562.smote.ranks$Rank.50kb,
				  vim.K562.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.K562.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")

#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
heatmap.2(t(rankdata),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          #margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #key.title = "Elastic-Net\nCoefficient",
          #keysize = 2,
          dendrogram="both",     # only draw a row dendrogram,
          Rowv = TRUE,
          Colv = TRUE,
          cexRow=1.5,
          cexCol=0.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          sepwidth=c(0.001,0.001),
          sepcolor="black",
          rowsep=1:4,
          colsep=0:nrow(rankdata)) 
```

# ICC

```{r}
vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
icc(vim.gm12878.smote, model = "twoway", type = "agreement")
